Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2020-05-02 manuscript/manuscript.tex
Gs changes

We first investigated the effects of the selected trait's genetic architecture
on temporal covariances and $G(t)$ by neutrally burning in a population for
$10N$ generations, and selecting on the trait with an exponential fitness
function. By using an exponential fitness function (a form of selection
multiplicative across sites), we ensure there is no build up of LD due to
selection and epistasis \parencite{Turelli1990-kd,Bulmer1980-zo}; this serves
as the simplest directional selection model of a trait to understand the
effects of genetic architecture on the statistics we have used in the paper.

@@

In our previous work, we did not investigate the affect of trait architecture
on our measure $G(t)$. Using the exponential fitness function simulations, we
also calculated $G(t)$ for each of the replicate simulations. We find that the
$G(t)$ trajectories can vary considerably across replicates depending on the
number of sites ($L$) determining the trait's value (Supplementary Figure
\ref{suppfig:sim-expfit-Gs}). When a trait is monogenic ($L \approx 1$), $G(t)$
trajectories vary considerably across replicate lines, as certain lines may not
contain the few selected alleles (top row of Supplementary Figure
\ref{suppfig:sim-expfit-Gs}). However, with a polygenic trait, ($L \ge 100$),
the $G(t)$ trajectories across replicates are all quite close as each replicate
contains an abundance of alleles that affect the trait's value (bottom rows of
Supplementary Figure \ref{suppfig:sim-expfit-Gs}). Comparing the simulated
$G(t)$ replicate trajectories of Supplementary Figure
\ref{suppfig:sim-expfit-Gs} with the \textcite{Barghi2019-qy} $G(t)$
trajectories in Figure \ref{fig:figure-1}B, we again confirm a finding of
\textcite{Barghi2019-qy}: that there is considerable genetic redundancy among
beneficial alleles. We should note that our simplified simulation routines are
slightly different from the \textcite{Barghi2019-qy} study in that the burnin
populations are all independent; however we expect the same qualitative result.

@@

Additionally, we wanted to ensure that our temporal covariances and $G(t)$
trajectories were robust to more complicated, but realistic fitness models. To
this end, we also simulated Gaussian stabilizing selection (GSS) on a trait
during burnin, with two optima shift routines: (1) sudden optima shifts of
$\mu_\text{sudden} = \{0.1\sigma, 0.5\sigma, 1\sigma\}$, and (2) very graduate
optima shifts of $\mu_\text{gradual} = \{0.001\sigma, 0.01\sigma\}$ per
generation using the same two population simulation scheme described above. We
used a polygenic architecture for these simulations ($L = 1000$ trait affecting
loci), and the optima shift began at five generations after a $10N$ generation.
Across our GSS simulations, we see the expected selection response
(Supplementary Material Figure \ref{suppfig:gss-zbar}).

>>>>

We first investigated the effects of the selected trait's genetic architecture
on temporal covariances and $G(t)$ by neutrally burning in a population for
$10N$ generations, and selecting on the trait with an exponential fitness
function. By using an exponential fitness function (\gc{corresponding
  to multiplicate}
selection across sites), we ensure there is no build up of LD due to
selection and epistasis \parencite{Turelli1990-kd,Bulmer1980-zo}
\gc{IS THIS PHRASED CORRECTLY, IS IT only in infinite pop that this holds?}; this serves
as the simplest directional selection model of a trait to understand the
effects of genetic architecture on the statistics we have used in the paper.

@@

In our previous work, we did not investigate the affect of trait architecture
on our measure $G(t)$. Using the exponential fitness function simulations, we
also calculated $G(t)$ for each of the replicate simulations. We find that the
$G(t)$ trajectories can vary considerably across replicates depending on the
number of sites ($L$) determining the trait's value (Supplementary Figure
\ref{suppfig:sim-expfit-Gs}). When a trait is
gc{reasonably} monogenic ($L \approx 1$), $G(t)$
trajectories vary considerably across replicate lines, as certain
lines may \gc{stochastically lose } %notcontain
the few \gc{copies
  of the} selected alleles (top row of Supplementary Figure
\ref{suppfig:sim-expfit-Gs}). However, with a polygenic trait, ($L \ge 100$),
the $G(t)$ trajectories across replicates are \gc{similar} as each
replicate %that affect the trait's value
contains an abundance of \gc{trait} alleles (bottom rows of
Supplementary Figure \ref{suppfig:sim-expfit-Gs}). Comparing the simulated
$G(t)$ replicate trajectories of Supplementary Figure
\ref{suppfig:sim-expfit-Gs} with the \textcite{Barghi2019-qy} $G(t)$
trajectories in Figure \ref{fig:figure-1}B, we again confirm a finding of
\textcite{Barghi2019-qy}: that there is considerable genetic redundancy among
beneficial alleles \gc{? Meaning lots of loci?}. We should note that our simplified simulation routines are
slightly different from the \textcite{Barghi2019-qy} study in that the burnin
populations are all independent; however we expect the same qualitative result.

@@

Additionally, we wanted to ensure that our temporal covariances and $G(t)$
trajectories were robust to more complicated, but realistic fitness models. To
this end, we also simulated Gaussian stabilizing selection (GSS) on a trait
during burnin, \gc{followed by one of two} two optima shift routines: (1) sudden optima shifts of
$\mu_\text{sudden} = \{0.1\sigma, 0.5\sigma, 1\sigma\}$, and (2) very graduate
optima shifts of $\mu_\text{gradual} = \{0.001\sigma, 0.01\sigma\}$ per
generation using the same two population simulation scheme described above. We
used a polygenic architecture for these simulations ($L = 1000$ trait affecting
loci), and the optima shift began at five generations after a $10N$
generation \gc{burnin}.
Across our GSS simulations, we see the expected selection response
(Supplementary Material Figure \ref{suppfig:gss-zbar}).

\gc{do you say what the effect size
  distribution is? Is it +/- again? How big is effect?}
